### 2008-03-16 trunk/SAiP/Module1/H3/doc/qualityattributes.tex
Update with more comments about scenario

>>>>

The scenarios may be further clarified in order to include the aspects of availability and performance, as shown below.

\begin{quote}
The customer browses the beer catalogue for descriptions and reviews and receives the result within 5 seconds 99\% of the time, 30 seconds 0,9\% of the time and more than 30 seconds 0,1\% of the time.

The customer selects appropriate beers for purchase and these are added to his shopping basket. When the customer checks out, payment is validated through the payment service within 30 seconds.
\end{quote}
